---
title: 'ESM 244 Lab 7 Parts 2-3: Text Cleaning, Mining, and Sentiment Analysis'
author: "Carlos Simms"
date: "2/21/2021"
output: html_document
---

# PART 2: Text Cleaning and Mining

### Attaching packages

```{r setup, include=TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE)
library(tidyverse) # Default.
library(tidytext)
library(textdata)
library(pdftools) # To read in and customize pdf documents. NOTE: This package does not work on R Bren Server V3.6...
library(ggwordcloud)
library(here)
```

### Reading in the Hobbit text pdf

```{r, cache = TRUE}
hobbit_text <- pdf_text(here("text", 
                             "the-hobbit.pdf")) # NOTE: To read in a pdf text document in R Cloud V4.0.3, you must first place it in a different folder within the .Rproj file.

hobbit_text_p34 <- hobbit_text[34]
hobbit_text_p34
```

### Converting the text into a tidy data frame

```{r}
hobbit_tidy <- data.frame(hobbit_text) %>% 
  mutate(text_full = str_split(hobbit_text, 
                               pattern = "\\n")) %>% # To tell R that anything with a "\n" (denoting new lines and/or indentations) that it should read them as so without "\n".
  unnest(text_full) %>% # To remove the "c()" vectoring.
  mutate(text_full = str_trim(text_full)) 
```

### Wrangling and converting the text into a tidy text format

```{r}
hobbit_df <- hobbit_tidy %>% 
  slice(-(1:125)) %>% 
  mutate(chapter = case_when(str_detect(text_full, 
                                        pattern = "Chapter") ~ text_full, 
                             TRUE ~ NA_character_)) %>% # To convert the "NA" values to a character class instead of a logical class.
  fill(chapter) %>% # To fill all "NA" values in the "chapter" column to the appropriate chapter value.
  separate(col = chapter, 
           into = c("ch", 
                    "no"), 
           sep = " ") %>% # Because the Hobbit text chapters are in Roman numerals, they must be separated to be read independently.
  mutate(chapter = as.numeric(as.roman(no))) # To mutate and read the character Roman numerals as numeric Roman numerals.
```

### Tokens

```{r}
hobbit_tokens <- hobbit_df %>% 
  tidytext::unnest_tokens(word, 
                          text_full) %>% 
  dplyr::select(-hobbit_text) # At this point, adding in a lot of packages may conflict with 'dplyr' - this may only be an issue in the R Bren Server V3.6...

hobbit_wordcount <- hobbit_tokens %>% 
  count(chapter, 
        word)

hobbit_wordcount
```

### Removing all 'stop_words' that exist in 'hobbit_tokens'

```{r}
hobbit_nonstop_words <- hobbit_tokens %>% 
  anti_join(stop_words) # To indicate what words you do not want to keep in the text data frame.

nonstop_counts <- hobbit_nonstop_words %>% 
  count(chapter, 
        word)

nonstop_counts
```

### Searching for the top five words in each chapter

```{r}
top_5_words <- nonstop_counts %>% 
  group_by(chapter) %>% 
  arrange(-n) %>% 
  slice(1:5)

ggplot(data = top_5_words, 
       aes(x = word, 
           y = n)) + 
  geom_col(fill = "blue") + 
  facet_wrap(~chapter, 
             scales = "free") + 
  coord_flip()
```

### Creating a word cloud

```{r}
ch1_top100 <- nonstop_counts %>% 
  filter(chapter == 1) %>% 
  arrange(-n) %>% 
  slice(1:100)

ch1_cloud <- ggplot(data = ch1_top100, 
                    aes(label = word)) + 
  geom_text_wordcloud(aes(color = n, 
                          size = n)) + 
  scale_size_area(max_size = 6)

ch1_cloud
```

# PART 3: Sentiment Analysis

### Using "afinn" lexicon - ranking on a scale from negative to positive five

```{r}
afinn_pos <- get_sentiments("afinn") %>% 
  filter(value > 2)

hobbit_afinn <- hobbit_nonstop_words %>% 
  inner_join(get_sentiments("afinn"))

afinn_counts <- hobbit_afinn %>% 
  count(chapter, 
        value)

afinn_means <- hobbit_afinn %>% 
  group_by(chapter) %>% 
  summarize(mean_afinn = mean(value))

ggplot(data = afinn_means, 
       aes(x = chapter, 
           y = mean_afinn)) + 
  geom_col() + 
  coord_flip()

# This gives us a method to assess the sentiments/emotions based on the positivity and negativtiy of the Hobbit text.
```

### Using "NRC" lexicon

```{r}
hobbit_nrc <- hobbit_nonstop_words %>% 
  inner_join(get_sentiments("nrc"))

hobbit_nrc_counts <- hobbit_nrc %>% 
  count(chapter, 
        sentiment)

ggplot(data = hobbit_nrc_counts, 
       aes(x = sentiment, 
           y = n)) + 
  geom_col() + 
  facet_wrap(~chapter) + 
  coord_flip()
```

END