---
title: 'ESM 244 Lab 7 Part 1: Useful Functions for Strings in stringr'
author: "Carlos Simms"
date: "2/21/2021"
output: html_document
---

### Attaching packages

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE)
library(tidyverse) # Default.
```

### Detecting string patterns with 'str_detect()' 

```{r}
vec <- c(" A Unicorn   Fish ", 
         "add   cornmeal", 
         "French FRIES", 
         "acorn Squash ")

str_detect(vec, 
           pattern = "corn")
```

```{r}
# Using 'str_detect()':

walk_subset <- starwars %>% 
  filter(str_detect(name, 
                    pattern = "walk"))

walk_subset

# Or use 'str_subset()':
```

### Replacing a string pattern with something else

```{r}
# Using 'str_replace()' to replace an existing string pattern with something else.

vec_bren <- str_replace(vec, 
                        pattern = "corn", 
                        replacement = "COOL")

vec_bren
```

### Replacing the pattern "Sky" with the pattern "TORNADO"

```{r}
sw_tornado <- starwars %>% 
  mutate(name = str_replace(name, 
                            pattern = "Sky", 
                            replacement = "TORNADO"))
```

### Using 'str_trim()' to remove excess leading and trailing whitespace from observation names

```{r}
str_trim(vec)
```

### Using 'str_squish()' to remove excess whitespace within observation names

```{r}
str_squish(vec)
```

```{r}
str_detect(vec, 
           pattern = "Corn") # Results in universal "FALSE" as R is case sensitive.
```

### Using 'str_to_*()'

```{r}
str_to_lower(vec) # To make all observation names lower case.

str_to_upper(vec) # To make all observation names upper case.

str_to_title(vec) # To make all observation names title case.
```

### Using all of the aforementioned in combination

```{r}
sw_combo <- starwars %>% 
  filter(str_detect(name, 
                    pattern = "Darth")) %>% 
  mutate(name = str_replace(name, 
                            pattern = "Darth", 
                            replacement = "LLAMA")) %>% 
  mutate(name = str_to_lower(name))

sw_combo
```

END